%--------------------------------------------------------------
%--------------------------------------------------------------
% Section 1 : Introduction
%--------------------------------------------------------------
%--------------------------------------------------------------
\chapter{Introduction}

%--------------------------------------------------------------
% Section 1.1 : Learning about MPTK
%--------------------------------------------------------------
\section{Learning about MPTK}
	
The Matching Pursuit Tool Kit (MPTK) provides a fast implementation of the Matching Pursuit algorithm for 
the sparse decomposition of multichannel signals such as audio signals. It comprises a library, standalone 
utilities and Matlab scripts.

MPTK provides an implementation of Matching Pursuit which is: 

\begin{my_itemize}
	\item \textbf{FAST:} e.g., extract 1.5 million atoms from a 1 hour long, 16kHz audio signal (15dB extracted) in 0.25x 
	real time on a Pentium IV@2.4GHz, out of a dictionary of 178M Gabor atoms. Such incredible speed makes it 
	possible to process ``real world'' signals.
	\item \textbf{FLEXIBLE:} multi-channel, various signal input formats, flexible syntax to describe the dictionaries 
	$\mapsto$ reproducible results, cleaner experiments. 
	\item OPEN: modular architecture $\mapsto$ add your own atoms ! Free distribution under the GPL. 
\end{my_itemize}

MPTK is mainly developed and maintained within the METISS Research Group \linebreak
(http://www.irisa.fr/metiss/) on audio signal processing, at the INRIA Research 
Institute (http://www.irisa.fr or http://www.inria.fr/rennes) in Rennes, France.

%--------------------------------------------------------------
% Section 1.2 : Reading this document
%--------------------------------------------------------------
\section{Reading this document}

This document describes the basic principles about how to download, install and use the Matching Pursuit Tool Kit. 
It is divided into two major sections : 

\begin{my_itemize}
	\item \textbf{\large Part \ref{getSrtd} : Getting started with MPTK}\\
		\underline{\emph{For Windows users :}} Read chapter \ref{MptkForWin} to learn how to download \& install MPTK\\
		\underline{\emph{For Linux users :}} Read chapter \ref{MptkForLin} to learn how to download \& install MPTK\\
		\underline{\emph{For Mac users :}} Read chapter \ref{MptkForMac} to learn how to download \& install MPTK\\
		$\mapsto$ You can skip to chapters \ref{MptkWithMatlab} \& \ref{MptkCmdLine} to understand the basic usage of MPTK
	\item \textbf{\large Part \ref{usrMan} : Advanced User Manual}\\
		Read chapter \ref{DownInstSources} to learn how to pre-build, build \& install MPTK from the source files\\
		Read chapters \ref{UseCmdLine} \& \ref{ListCmdLine} to learn how to use MPTK with command line tools\\
		Read chapters \ref{UseMatlabFunc} \& \ref{ListMatlabFunc} to learn how to use MPTK within Matlab
\end{my_itemize}

\clearpage